3. Analyses Plan

### 2021-06-24 reports/01_dataGMTV.Rmd
recalculate gini using the stock instead of the endowments

noPunish10[,
           gini2 := Gini(c(tokens, other1, other2, other3)),
           by = .(subj_id, per)]

noPunish10[order(gr_id, per),
           .(exp_num, gr_id, per, subj_id, # IDs
             tokens, other1, other2, other3, gdp, #endowments
             putin, pu1, pu2, pu3, sum, mean, share, # contributions
             gini, gini2
           )] %>% 
  head(n = 15) %>%
  kbl() %>% 
  # scroll_box(height = "200px") %>%
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)

@@

GMTV <- noPunish10[order(gr_id, per),
           .(treatment = "noPunish10", 
             session.code = exp_num,
             groupID = gr_id, 
             round = per,
             contribution = sum,
             endowment = gdp,
             share = mean, # share,
             stock = (gdp + ceiling(sum/4*1.5)*4-sum),
             gain = (ceiling(sum/4*1.5)*4-sum),
             gini = gini2,
             bot_active = 0,
             # disaster = 0,
             # EWE = 0,
             noComprehension = 0)] %>% unique()

>>>>

# calculate gini based on endowments (as GMTV did)
noPunish10[,
           gini2 := Gini(c(tokens, other1, other2, other3)),
           by = .(subj_id, per)]

# calculate gini based on stock (i.e. end of period earnings)
noPunish10[, stock0 := tokens - putin + sum/4]
noPunish10[, stock1 := other1 - pu1 + sum/4]
noPunish10[, stock2 := other2 - pu2 + sum/4]
noPunish10[, stock3 := other3 - pu3 + sum/4]

noPunish10[, 
           gini3 := Gini(c(stock0, stock1, stock2, stock3)),
           by = .(subj_id, per)]

# show table
noPunish10[order(gr_id, per),
           .(exp_num, gr_id, per, subj_id, # IDs
             tokens, other1, other2, other3, gdp, #endowments
             putin, pu1, pu2, pu3, sum, mean, share, # contributions
             gini, gini2, gini3
           )] %>% 
  head(n = 15) %>%
  kbl() %>% 
  # scroll_box(height = "200px") %>%
  kable_paper("hover", 
              full_width = TRUE,
              fixed_thead = TRUE)

@@

GMTV <- noPunish10[order(gr_id, per),
           .(treatment = "noPunish10", 
             session.code = exp_num,
             groupID = gr_id, 
             round = per,
             contribution = sum,
             endowment = gdp,
             share = mean, # share,
             stock = (gdp + ceiling(sum/4*1.5)*4-sum),
             gain = (ceiling(sum/4*1.5)*4-sum),
             gini = gini3,
             bot_active = 0,
             # disaster = 0,
             # EWE = 0,
             noComprehension = 0)] %>% unique()

### 2021-06-24 reports/02_dataProcessing.Rmd
recalculate gini using the stock instead of the endowments

```{r calcGini}
# it would make more sense to calculate the stocks' gini but gaechter et al use the endowments
var = names(subset) %>% str_subset(pattern = "player\\.endowment$")
gini = subset[,
              lapply(.SD, Gini, na.rm=TRUE), 
                by = cluster, 
                .SDcols=var
              ]
Gini <- melt(gini, id.vars = cluster, measure.vars = var)

>>>>

```{r calcGini}
# note that GMTV used start of period earnnings, i.e. endowments. We use end of period earnings, i.e. stock.
# this adjustment has been considered in our processing of GMTVs data.

var = names(subset) %>% str_subset(pattern = "player\\.stock$")
gini = subset[,
              lapply(.SD, Gini, na.rm=TRUE), 
                by = cluster, 
                .SDcols=var
              ]
Gini <- melt(gini, id.vars = cluster, measure.vars = var)

### 2021-06-24 reports/03_dataAnalyses.Rmd
recalculate gini using the stock instead of the endowments

```{r readData}
load(file="../data/processed/rda/GMTV2017.rda")          # read GMTV
load(file="../data/processed/rda/GMTV2017_R1.rda")       # read GMTVFirstRound
load(file="../data/processed/rda/GMTV2017_COVS.rda")     # read GMTVCovariates
load(file="../data/processed/rda/replication2021.rda")       # read replication
load(file="../data/processed/rda/replication2021_R1.rda")    # read replicationFirstRound
load(file="../data/processed/rda/replication2021_COVS.rda")  # read replicationCovariates
```

>>>>

```{r readData}
base::load(file="../data/processed/rda/GMTV2017.rda")              # read GMTV
base::load(file="../data/processed/rda/GMTV2017_R1.rda")           # read GMTVFirstRound
base::load(file="../data/processed/rda/GMTV2017_COVS.rda")         # read GMTVCovariates
base::load(file="../data/processed/rda/replication2021.rda")       # read replication
base::load(file="../data/processed/rda/replication2021_R1.rda")    # read replicationFirstRound
base::load(file="../data/processed/rda/replication2021_COVS.rda")  # read replicationCovariates
```
